Model-based variable selection for regression with highly correlated variables.

### 2014-04-28 www/article13.tex
up ident
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@559 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

	If the sufficient condition is not satisfied but we have different variances for $\boldsymbol{X}_f$ and $\boldsymbol{X}_r$, then we don't have identifiability but reverse regressions don't give the same results as the true model, as illustrated in the well-known salary discrimination study \cite{goldberger1984reverse} and explained in books and papers (\cite{leamer1978least},\cite{cameron2005microeconometrics}).

	Remark : the uncrossing constraint ($I_2\cap I_1 = \emptyset$) significantly reduces the number of feasible models and thus increases identifiability (because it also reduces the number of models equivalent in interpretation).

>>>>

	In the followings, $N_{11}$ and $N_{12}$ Gaussian (multivariate or not). $\boldsymbol{X}_r$ is here supposed to be univariate (identifiability in such a case will be generalisable).
		\begin{eqnarray}
			f(\boldsymbol{X_f})&=& p_{11} N_{11}+p_{12}N_{12}\\
			\boldsymbol{X}_r&=&\boldsymbol{X}_f\boldsymbol{\alpha}_r +\boldsymbol{\varepsilon}_r \\
			f(\boldsymbol{X}_r)&=&p_{11}(N_{11}+\boldsymbol{\varepsilon})+p_{12}(N_{12}+\boldsymbol{\varepsilon}) \\
			f(\boldsymbol{X}_r|\boldsymbol{X}_f)&=&\boldsymbol{\varepsilon}\\
			f(\boldsymbol{X}_r,\boldsymbol{X}_f)&=&f(\boldsymbol{X}_r|\boldsymbol{X}_f)f(\boldsymbol{X}_f)=f(\boldsymbol{X}_f|\boldsymbol{X}_r)f(\boldsymbol{X}_r) \\
			f(\boldsymbol{X}_f|\boldsymbol{X}_r)&=&\frac{f(\boldsymbol{X}_r|\boldsymbol{X}_f)f(\boldsymbol{X}_f)}{f(\boldsymbol{X}_r)} \\
			&=&\frac{(p_{11} N_{11}+p_{12}N_{12})\boldsymbol{\varepsilon}}{p_{11}(N_{11}+\boldsymbol{\varepsilon})+p_{12}(N_{12}+\boldsymbol{\varepsilon})} \textrm{ with }p_{11}+p_{12}=1\\
			&=&\frac{(p_{11} N_{11}+p_{12}N_{12})\boldsymbol{\varepsilon}}{(p_{11} N_{11}+p_{12}N_{12})+\boldsymbol{\varepsilon}}
		\end{eqnarray}
	So we have a quotient of two multivariate Gaussian mixtures and the question is to know if it is Gaussian (in such a case we wouldn't have identifiability).
If $\boldsymbol{X}_f$ is a Gaussian mixture with $K>1$ distinct components, then so will be $\boldsymbol{X}_r$.
	We know that for a Gaussian multivariate distribution $(\boldsymbol{X}_r,\boldsymbol{X}_f)$ the conditional distributions $(\boldsymbol{X}_r|\boldsymbol{X}_f)$ and $(\boldsymbol{X}_f|\boldsymbol{X}_r)$ are both Gaussian.

		We decompose the joint distribution based on the components $k$.

	\begin{eqnarray}
			f(\boldsymbol{X}_r)&=&f(\boldsymbol{X}_f\boldsymbol{\alpha}_r +\boldsymbol{\varepsilon}_r) (MG to define explicitely) \\
			\forall 1\leq j \leq K,  f(\boldsymbol{X}_r|k=j)&=& Gaussian to define
			\end{eqnarray}
		\begin{equation}
			f(\boldsymbol{X}_r,\boldsymbol{X}_f)= \sum_{j=1}^K p_jf(\boldsymbol{X}_r,\boldsymbol{X}_f|k=j)
	\end{equation}
			where  $\forall 1\leq j \leq K$, $ f(\boldsymbol{X}_r,\boldsymbol{X}_f|k=j)$  is Gaussian multivariate  and thus
			\begin{equation}
			f(\boldsymbol{X}_r,\boldsymbol{X}_f)= \sum_{j=1}^K p_jf(\boldsymbol{X}_f|\boldsymbol{X}_r,k=j)f(\boldsymbol{X}_r|k=j)
	\end{equation}
				where  $\forall 1\leq j \leq K$, $ f(\boldsymbol{X}_r,\boldsymbol{X}_f|k=j)$  is Gaussian and $f(\boldsymbol{X}_f|\boldsymbol{X}_r,k=j)$ is Gaussian

				Now we know that $\forall 1\leq j \leq K$,  $f(\boldsymbol{X}_f|\boldsymbol{X}_r,k=j)$ is Gaussian:
				\begin{equation}
				f(\boldsymbol{X}_f|\boldsymbol{X}_r)=\sum_{j=1}^Kp_jf(\boldsymbol{X}_f|\boldsymbol{X}_r,k=j)
				\end{equation}
				is a Gaussian mixture, so we have identifiability of the model even for trivial sub-regression if we keep the constraint to have distinct components.
			%f(\boldsymbol{X}_r,\boldsymbol{X}_f)&=& sum_{j=1}^K

%	If the sufficient condition is not satisfied but we have different variances for $\boldsymbol{X}_f$ and $\boldsymbol{X}_r$, then we don't have identifiability but reverse regressions don't give the same results as the true model, as illustrated in the well-known salary discrimination study \cite{goldberger1984reverse} and explained in books and papers (\cite{leamer1978least},\cite{cameron2005microeconometrics}).
%	
	Remark : the uncrossing constraint ($I_r\cap I_f = \emptyset$) significantly reduces the number of feasible models and thus increases identifiability (because it also reduces the number of models equivalent in interpretation).
